\texttt{timeline} Documentation

### 2016-06-17 docs/documentation/documentation.tex
update documentation

\begin{itemize}
\item
\textbf{go to the vagrant folder:} \texttt{cd vagrant/}
\item
\textbf{start vagrant:} \texttt{vagrant up}
\item
\textbf{start our website:} start a browser and go to \texttt{http://localhost:5000/}
\end{itemize}

@@

\subsubsection*{Time Series Plot}
\begin{itemize}
 \item[] \textbf{Description:} This function generate the data to visualize a simple time series plot, with no additional given start and end date.
\end{itemize}

\subsubsection*{Add Rolling Mean}
\begin{itemize}
 \item[] \textbf{Description:} This function generate the data to visualize a simple time series plot with an rolling mean.
\end{itemize}

\subsubsection*{Add Rolling Std}
\begin{itemize}
 \item[] \textbf{Description:} This function generate the data to visualize a simple time series plot with an rolling standard deviation.
\end{itemize}

\subsubsection*{Auto Correlation Plot}
\begin{itemize}
 \item[] \textbf{Description:} This function generate the data to visualize a auto correlation time series plot with the \texttt{max\_lag} parameter.
\end{itemize}

\subsubsection*{Forecasting Eval Plot}
\begin{itemize}
 \item[] \textbf{Description:} This function generate the data to visualize a forecasting time series plot.
\end{itemize}

\subsubsection*{Build Data Object}
\begin{itemize}
 \item[] \textbf{Description:} This function build the object for all other functions in this class. The object consists of a date and a value.
\end{itemize}

>>>>

\begin{itemize}
\item
\textbf{go to the vagrant folder:} \texttt{cd vagrant/}
\item
\textbf{start vagrant:} \texttt{vagrant up} (the first time can take a long time, because of the new downloaded and installed dependencies)
\item
\textbf{start our website:} start a browser and go to \texttt{http://localhost:5000/}
\end{itemize}

@@

\subsubsection*{Time Series Plot:}
\begin{itemize}
 \item[] \textbf{Description:} This function generate the data to visualize a simple time series plot, with no additional given start and end date.
We iterate through all data from the data set, the title will be set and we return a object with a title, the x accessor, the date, the y accessor, the value,
the data, and the legend.
\end{itemize}

\subsubsection*{Add Rolling Mean:}
\begin{itemize}
 \item[] \textbf{Description:} This function generate the data to visualize a simple time series plot with an rolling mean. 
 We calculate the rolling mean and generate the data object with the data and the legend.
\end{itemize}

\subsubsection*{Add Rolling Std:}
\begin{itemize}
 \item[] \textbf{Description:} This function generate the data to visualize a simple time series plot with an rolling standard deviation. 
 We calculate the rolling standard deviation and generate the data object with the data and the legend.
\end{itemize}

\subsubsection*{Auto Correlation Plot:}
\begin{itemize}
 \item[] \textbf{Description:} This function generate the data to visualize a auto correlation time series plot with the \texttt{max\_lag} parameter.
 We iterate through all data from the data set in range from 1 to the \texttt{max\_lag} and generate the data object
\end{itemize}

\subsubsection*{Forecasting Eval Plot:}
\begin{itemize}
 \item[] \textbf{Description:} This function generate the data to visualize a forecasting time series plot.
\end{itemize}

\subsubsection*{Build Data Object:}
\begin{itemize}
 \item[] \textbf{Description:} This function build the object for all other functions in this class. The object consists of a date and a value.
\end{itemize}
